Figures

### 2020-04-15 manuscript/figures.Rmd
point to defn of geometric depth

```{r 02_depth_model_importance, fig.cap = "Importance plot for random forest variables showing increase in mean square error. Higher values indicate greater importance to model predictions.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/02_depth_model_importance-1.pdf")
```

>>>>

```{r 02_depth_model_importance, fig.cap = "Importance plot for random forest variables showing increase in mean square error. Higher values indicate greater importance to model predictions. See Equation 1 for a definition of geometric max depth.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/02_depth_model_importance-1.pdf")
```
